### 2016-11-07 paper2.tex
Added short captions for tables
Added all TOC elements

\begin{abstract}
    We present the first cosmological galaxy evolved using the modern smoothed
    particle hydrodynamics (SPH) code \textsc{GASOLINE2} with superbubble
    feedback.  We show that superbubble-driven galactic outflows powered by Type
    II supernovae alone can produce $\rm{L^*}$ galaxies with flat rotation
    curves with circular velocities $\sim 200\; \rm{km/s}$, low bulge-to-disc
    ratios, and stellar mass fractions that match observed values from high
    redshift to the present.  These features are made possible by the high mass
    loadings generated by the evaporative growth of superbubbles.  Outflows are
    driven extremely effectively at high redshift, expelling gas at early times
    and preventing overproduction of stars before $z=2$.  Centrally
    concentrated gas in previous simulations has often lead to unrealistically
    high bulge to total ratios and strongly peaked rotation curves.  We show that
    supernova-powered superbubbles alone can produce galaxies that agree well
    with observed properties without the need for additional feedback mechanisms
    or increased feedback energy.   We present additional results arising from
    properly modelled hot feedback.
\end{abstract}

@@

\section{Results}
\begin{table*}
    \begin{tabular}{ c c c c c c c}
        \hline
        Simulation & $M_{vir}$ & $M_{gas}$ &
        $M_{star}$  &$M_{bary,0.1vir}$ & $M_{bulge}$ & $M_{disc}$ \\
        \hline
        No Feedback & $7.94\times10^{11}$ & $6.21\times10^{10}$ &
        $7.42\times10^{10}$ & $8.09\times10^{10}$ & $9.34\times10^{9}$ &
        $2.88\times10^{10}$\\
        Blastwave Feedback & $7.99\times10^{11}$ & $8.05\times10^{10}$ &
        $5.11\times10^{10}$ & $7.94\times10^{10}$ & $8.09\times10^{9}$ &
        $1.75\times10^{10}$ \\
        Superbubble Feedback & $8.02\times10^{11}$ & $1.19\times10^{11}$ &
        $1.84\times10^{10}$ & $6.25\times10^{10}$ & $1.14\times10^{9}$ &
        $1.15\times10^{10}$ \\
        Superbubble, $2\times10^{51} erg/SN$ & $7.96\times10^{11}$ &
        $1.20\times10^{11}$ & $1.09\times10^{10}$ &  $4.92\times10^{10}$ & 
        $5.96\times10^{8}$ & $6.98\times10^9$\\
    \end{tabular}
    \caption{Halo components at $z=0$. $M_{disc}$ and $M_{bulge}$ are the
    determined by the angular momentum of the stars (as detailed below).  All
    masses are in $M_\odot$.}
    \label{properties}
\end{table*}

>>>>

\begin{abstract}
        \addcontentsline{toc}{section}{Abstract}
    We present the first cosmological galaxy evolved using the modern smoothed
    particle hydrodynamics (SPH) code \textsc{GASOLINE2} with superbubble
    feedback.  We show that superbubble-driven galactic outflows powered by Type
    II supernovae alone can produce $\rm{L^*}$ galaxies with flat rotation
    curves with circular velocities $\sim 200\; \rm{km/s}$, low bulge-to-disc
    ratios, and stellar mass fractions that match observed values from high
    redshift to the present.  These features are made possible by the high mass
    loadings generated by the evaporative growth of superbubbles.  Outflows are
    driven extremely effectively at high redshift, expelling gas at early times
    and preventing overproduction of stars before $z=2$.  Centrally
    concentrated gas in previous simulations has often lead to unrealistically
    high bulge to total ratios and strongly peaked rotation curves.  We show that
    supernova-powered superbubbles alone can produce galaxies that agree well
    with observed properties without the need for additional feedback mechanisms
    or increased feedback energy.   We present additional results arising from
    properly modelled hot feedback.
\end{abstract}

@@

\section{Results}
\begin{table*}
    \begin{tabular}{ c c c c c c c}
        \hline
        Simulation & $M_{vir}$ & $M_{gas}$ &
        $M_{star}$  &$M_{bary,0.1vir}$ & $M_{bulge}$ & $M_{disc}$ \\
        \hline
        No Feedback & $7.94\times10^{11}$ & $6.21\times10^{10}$ &
        $7.42\times10^{10}$ & $8.09\times10^{10}$ & $9.34\times10^{9}$ &
        $2.88\times10^{10}$\\
        Blastwave Feedback & $7.99\times10^{11}$ & $8.05\times10^{10}$ &
        $5.11\times10^{10}$ & $7.94\times10^{10}$ & $8.09\times10^{9}$ &
        $1.75\times10^{10}$ \\
        Superbubble Feedback & $8.02\times10^{11}$ & $1.19\times10^{11}$ &
        $1.84\times10^{10}$ & $6.25\times10^{10}$ & $1.14\times10^{9}$ &
        $1.15\times10^{10}$ \\
        Superbubble, $2\times10^{51} erg/SN$ & $7.96\times10^{11}$ &
        $1.20\times10^{11}$ & $1.09\times10^{10}$ &  $4.92\times10^{10}$ & 
        $5.96\times10^{8}$ & $6.98\times10^9$\\
    \end{tabular}
    \caption[Halo Components at $z=0$ for different feedback models]{Halo
    components at $z=0$. $M_{disc}$ and $M_{bulge}$ are the determined by the
    angular momentum of the stars (as detailed below).  All masses are in
    $M_\odot$.}
    \label{properties}
\end{table*}

### 2016-11-07 paper4.tex
Added all TOC elements

\begin{abstract}
    Recent analysis \citep{McGaugh2016} of the SPARC galaxy sample found a
    surprisingly tight relation between the radial acceleration inferred from
    the rotation curves, and the acceleration due to the baryonic components of
    the disc.  It has been suggested that this relation may be evidence for new
    physics, beyond $\Lambda CDM$.  In this letter we show that the 18
    galaxies from the MUGS2 match the SPARC acceleration relation. These
    cosmological simulations of star forming, rotationally supported discs were
    simulated with a {\sc WMAP3} $\Lambda CDM$ cosmology, and match the SPARC
    acceleration relation with less scatter than the observational data.  These
    results show that this acceleration law is a consequence of
    dissipative collapse of baryons, rather than being evidence for exotic
    dark-sector physics or new dynamical laws.
\end{abstract}

>>>>

\begin{abstract}
        \addcontentsline{toc}{section}{Abstract}
    Recent analysis \citep{McGaugh2016} of the SPARC galaxy sample found a
    surprisingly tight relation between the radial acceleration inferred from
    the rotation curves, and the acceleration due to the baryonic components of
    the disc.  It has been suggested that this relation may be evidence for new
    physics, beyond $\Lambda CDM$.  In this letter we show that the 18
    galaxies from the MUGS2 match the SPARC acceleration relation. These
    cosmological simulations of star forming, rotationally supported discs were
    simulated with a {\sc WMAP3} $\Lambda CDM$ cosmology, and match the SPARC
    acceleration relation with less scatter than the observational data.  These
    results show that this acceleration law is a consequence of
    dissipative collapse of baryons, rather than being evidence for exotic
    dark-sector physics or new dynamical laws.
\end{abstract}
